%-------------------------
% Resume in Latex
% Author : Umang Sehgal
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://umangsehgal.com/}{\Large Umang Sehgal}} & Email : \href{mailto:umang93@uw.edu}{umang93@uw.edu}\\
  \href{http://umangsehgal.com/}{http://www.umangsehgal.com} & Mobile : (206)972-8543 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Master of Science in Information Management;  GPA: 3.80}{Sep. 2017 -- Jun. 2019}
    \resumeSubheading
      {LNM Institute of Information Technology}{Jaipur, India}
      {Bachelor of Technology in Computer Science and Engineering}{Jul. 2012 -- Jun. 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Evive Health}{Bangalore, India}
      {Software Engineer}{June 2016 - June 2017}
      \resumeItemListStart
        \resumeItem{Weight Watcher}
          {Built this service for tracking weight activities, notifying users with emails and SMSes using third-party APIs, calculate the incentives and perform periodic monitoring and statistical analysis.}
        \resumeItem{IVR 2.0}
          {Revamped the exisiting voice based interaction with the Nexmo Voice API for obtaining Health Information and wrapped the interaction with Cassandra and Elastic Search. [Received Appreciation for well-written and bug free code]}
        \resumeItem{Care to Go}
          {Implemented the service for 'Second Opinion' recommendation system for Evive's clients, currently used throughout the care suggestion process}
        \resumeItem{Incremental ETL}
          {Built an asynchronous ETL framework to perform incremental data load from various data vendors. This reduced loading times from 4 hours for full to under 28 minutes for incremental load.}
        \resumeItem{Survey Response Aggregator}
          {Created a state machine framework which was used to drive a survey. The state machine persisted the user’s states to enable resuming the survey later.}
        \resumeItem{Multiple Small Enterprise Applications}
          {Created several enterprise web applications, working with Java (8), Cassandra,
Redis, Spring Boot, ElasticSearch, Git etc following agile processes including scrum and test-driven development}      	\resumeItemListEnd

    \resumeSubheading
      {Korea Advanced Institute of Science and Technology}{Daejeon, South Korea}
      {Research Intern}{May 2015 - Jul 2015}
      \resumeItemListStart
        \resumeItem{OncoSearch}
          {Wrote and tested map reduce jobs to distribute the Cancer Gene Search Engine improving performance by 12 percent.}
        \resumeItem{Korean Sign Langugage Translator}
          {Wrote a pipeline to construct and collate corpus for Korean Sign Language Translation}
      \resumeItemListEnd

    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Research and Teaching Assistant}{Oct 2017 - Present}
      \resumeItemListStart
        \resumeItem{Student Researcher - Code and Cognition Lab}
          {Working with Prof. Andrew J. Ko and PhD. Student Dastyni Loksa on formulating problem-solving behaviors through qualitative coding of self-regulation and journaled projects}
        \resumeItem{Teaching Assistant - Intro to Data Science (INFO 370)}
          {Create Readings, Evaluate and Grade Code Submissions, Redesign Curriculum. Apart from this, we are working as a team to define the Data Science process in a set of 10 week modules with topics like decision theory, data cleaning, modelling, visualization and scaling.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Database Principles}
      {The course involves a project on data summarization, sampling, approximate query processing [In Progress]}
    \resumeSubItem{SimPark}
      {Designed a mobile application that helps users find parking through crowdsourcing}
    \resumeSubItem{Coping Mechanisms Recommender}
      {Analysis and Recommendation of coping mechanisms in dementia caregiving}
    \resumeSubItem{DroidMic}
      {Converts your android phone into microphone for use at conferences!}
  \resumeSubHeadingListEnd


%--------COURSEWORK------------
\section{Graduate Coursework}
  \resumeSubHeadingListStart
    \item[]{
      \textbf{School of Computer Science}{: Database Principles, Human Computer Interaction}\\
      \textbf{Information School}{: Analytic Methods, Ethics in Data Science}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item[]{
      \textbf{Languages}{: Java, R, Python, SQL}
      \hfill
      \textbf{Technologies}{: Cassandra, Redis, AWS, JUnit, Maven, Git}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
